\documentclass[11pt]{resume}

\title{Full resume}
\usepackage{hyperref}
\usepackage{graphicx}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    pdfborder={0 0 0},
}
\newcommand{\memph}[1]{#1}
%\newcommand{\memph}[1]{\textbf{#1}}
\begin{document}
\topmargin=10mm
\vspace{-2em}
\begin{resume}
\section{\mysidestyle Academic Achievements}

\begin{list2}
\item Ranked \textbf {6\textsuperscript{th}} in the department among 140 students on CPI basis. \memph Pursuing a Minor Degree in Computer Science and Engineering.
\item Secured two \textbf {AP Grades} for being in the top 1\% of the courses \textbf{Basic Biology} and \textbf{Computer Programming and Utilization}.
\item Cleared the first two rounds of the \textbf{Astronomy Olmypiad} and was amongst the \textbf{top 10} at the \textbf {Astronomy OCSC} (Orientation Cum Selection Camp) for the International Olympiad for Astronomy and Astrophysics '14.
\item Cleared the first selection round of the \textbf{Physics Olympiad (NSEP)} and \textbf{Chemistry Olympiad (NSEC)}.
\item Secured an \textbf{All India Rank of 93} in \textbf{JEE Advanced '14}
and an All India Rank of \textbf{34} in \textbf{JEE Mains '14}.
\item Secured a \textbf{National Rank of 2} in \textbf{ICSE '12} and was the \textbf{city topper} in  JEE Advanced '14, JEE Mains '14, CBSE '14 and KVPY '14.
\item Won the \textbf {Kishore Vaigyanik Protsahan Yojana '14 (KYPY)} Fellowship Award with an All India Rank of 30.
\item Won the \textit{General Proficiency Prize} for 10 consecutive years in school. Was awarded by the \textbf {Army Welfare Education Society} for the \textit{best academic performance} in Army Schools in CBSE '14.
\item Secured 430 marks out of 450 in \textbf{BITSAT '14}
\end{list2}

% Work Experience
\section{\mysidestyle Work Experience}
\textbf{Senior Backend Developer}, \textsl{Pickup} \hfill \textbf{March '14 - Present}

\begin{list2}
\item Developing and implementing the backend for a recently launched startup - \textit {Pickup}, a ridesharing service.
\item Built \textbf {RESTful APIs}, designed an \textbf {ER Model Database} in \textbf {PHP} using the \textit {MVC Framework} \textbf{Laravel 4}. Developing algorithms for the same.
\end{list2}

\textbf{In-sem Internship}, \textsl{Codechef} \hfill \textbf{January '15 - Feburary '15}\\
\vspace{-4mm}
\begin{list2}
\item Built and mantained a \textbf{question bank} as a part of \textbf {Codechef for Schools}, an initiative to help high school students start competitive programming.
\item Wrote and reviewed \textbf{editorials} for the recently added problems on Codechef.
\end{list2}

\section{\mysidestyle Positions of Responsibility}
\textbf{Convener}, \textit{Web and Coding Club - IIT Bombay} \hfill \textbf{April '14 - Present}\\

\vspace{-4mm}
\begin{list2}
\item \textbf{Coordinating events} of one of the largest programming clubs in India aimed at inspiring students to take up programming as a hobby.
\item Organised institute-wide workshops to \textbf{train more than 100 students} in MIT-Scratch and Linux Essentials.
\end{list2}

\textbf{Coordinator}, \textit{Mood Indigo - IIT Bombay} \hfill \textbf{July '15 - Present}\\
\vspace{-4mm}
\begin{list2}
\item Working as part of a team to develop \textbf{Web and Android applications} for Mood Indigo, Asia's largest college cultural festival. 
\end{list2}
\pagebreak
\textbf{Mess Secretary}, \textit{Hostel 15 - IIT Bombay} \hfill \textbf{'14 - '15}\\
\vspace{-4mm}
\begin{list2}
\item Worked as a secretary to manage Mess affairs and voice student's opinion to the Mess Staff.
\end{list2}

\vspace{-2.5mm}

\section{\mysidestyle Programming Skills}
\begin{list2}
\item \textbf{Languages:} PHP (with Laravel 4), C/C++, Python (with Django and OpenCV), Java (with Android), JavaScript (with NodeJS and AngularJS), Arduino, Bash, \LaTeX
\item \textbf{Tools:} NgSpice, Adobe Photoshop, AutoCAD, Git, MATLAB/Octave, Processing
\end{list2}


\vspace{-1em}

\section{\mysidestyle Technical Achievements} 
\begin{list2}
\item Adjudged the \textbf{Runner Up} (as part of a 4-person team) at the \textbf{Microsoft code.fun.do Hackathon '15}

\item Stood \textbf {7\textsuperscript{th}} in the country in \textbf {Technothlon '10} and represented my school with a teammate in \textbf {Techniche '10, IIT Guwahati}. 

\item Attended a 2 week long workshop \textbf{Infosys, Catch Them Young} and won the best group software award. 

\item Stood \textbf {1\textsuperscript{st}} among 200 freshmen at \textbf {WnCC - Scratch Day '14}. Stood \textbf {2\textsuperscript{nd}} among 100 freshmen at \textbf {WnCC - Website Making '14} for my \href{https://home.iitb.ac.in/~140070017}{personal homepage}.

\item Took part in a week long workshop by \textbf {Muktangan Science Exploratory} on introduction to basic science in April '10.

\item Built an RC controlled robot and an Autonomous Line Follower under the \memph Electronics Club - IIT Bombay. Mentored a team of freshmen for the same.

\end{list2}

\vspace{-1em}

% Achievements
\section{\mysidestyle Relevant Courses}
\begin{list2}
\item \textbf {Electrical Engineering} :- Electronic Devices and Circuits, Network Theory, Basic Electronics and Electrical Systems 
\item \textbf {Computer Science} :- Data Structures and Algorithms, Computer Networks, Machine Learning (via \href{https://coursera.org}{coursera}) and Aritifical Intelligence (via \href{https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-034-artificial-intelligence-fall-2010/}{MIT OCW})
\item \textbf {Physics and Mathematics} :- Quantum Mechanics, Electromagnetism, Calculus, Linear Algebra, Differential Equations(I and II) and Complex Analysis.
\end{list2}

\vspace{-1em}

\section{\mysidestyle Projects}
\textbf{Pyraminx Utility Kit} \hfill \textbf{Spring '15}\\
\textsl{Prof. Kavi Arya} \hfill \textsl{CS 101 Project}\\
\vspace{-4mm}
\begin{list2}
\item Implemented \textbf{BFS graph algorithm and AVL trees} to derive mathematical results about the \textbf{optimal solutions of a Pyraminx}, a tetrahedron Rubiks Cube style puzzle.
\item Used C++ and Allegro to design an interface to help solve pyraminx optimally, find cube algorithms and generate solve analysis.
\item Designed an Android app implementing \textbf{image processing techniques} to read pyraminx configurations and send it to a Java server to be solved.
\end{list2}
\textbf{Bluetooth Mesh Network} \hfill \textbf{Summer '15}\\
\textsl{Web and Coding Club - IIT Bombay} \hfill \textsl{Institute Technical Summer Project}\\
\vspace{-4mm}
\begin{list2}
\item Made an \textbf{Android app} which implements \textbf{routing via Bluetooth} using a \textbf{Gnutella style flooding algorithm}.
\item Optimized the routing using graph algorithms and routing tables.
\end{list2}
\pagebreak

\vspace{-1em}
\textbf{Holographic Touch Screen} \hfill \textbf{Summer '15}\\
\textsl{Electronics Club - IIT Bombay} \hfill \textsl{Institute Technical Summer Project}\\
\vspace{-4mm}
\begin{list2}
\item Designed an \textbf{Infrared LED lined frame} interfaced with \textbf{Arduino} to determine the precise location of an object placed in this frame.
\item Used this \textbf{frame as a touch screen} for a \textbf{hologram} created using parabolic and plane mirror and an LCD display as the object.
\end{list2}

\textbf{LED Tetris Board} \hfill \textbf{Autumn '14}\\
\textsl{Electronics Club - IIT Bombay} \hfill \textsl{Techify Your Room}\\
\vspace{-4mm}
\begin{list2}
\item Designed a playable compact game of Tetris using two \textbf{8x8 LED grids}.
\item \textbf{Arduino} used for control via software multiplexing.
\end{list2}

\textbf{Radar Remote Controlled Car} \hfill \textbf{Spring '15}\\
\textsl{Electronics Club - IIT Bombay} \hfill \textsl{Techify Your Room}\\
\vspace{-4mm}
\begin{list2}
\item Designed a radar using servo motors and an ultrasonic sensor. \textbf{Data plotted using Processing}. Attached to an RC car to enable obstacle detection.
\end{list2}


\section{\mysidestyle Personal Projects}

\begin{list2}
\item \href{httpss://bugzilla.mozilla.org/user_profile?login=kalpeshk2011\%40gmail.com}{Contributing} to \textbf{Mozilla}, via bug fixes in Firefox Core, Firefox OS, Toolkit.
\item Active member on \textbf{Github} with a number of personal projects in \textsl{image processing, Python scripting, BASH, NodeJS and Javscript}.
\item A \textsl{Django} project to determine one's \textbf{Department Rank} using crowd sourcing.
\item A \textsl{Python/OpenCV, BASH} project to \textbf{detect finger contours} and \textbf{execute corresponding launcher application}.
\item \textsl{Python} scripts to \textbf{scrape music, lyrics and song metadata} off the internet.
\item A set of \textsl{Python} scripts to scrape e-mails and \textbf{automate e-receipt sending} for College of Engineering Pune, Mock United Nations.

\item A \textbf{Geography themed quiz game} in \textsl{Java} operating on a \textsl{MySQL} database containing data about countries.
\item A \textsl{NodeJS} \textbf{chat server} using socket.io
\item A number of games such as \textbf{Minesweeper, Reversi, Peg Solitaire} and some \textbf{basic Physics simulations} in \textsl{JavaScript} using DOM manipulations
\item A Gauss Rifle using Neodymium magnets as a part of Technothlon '10.
\end{list2}
\section{\mysidestyle Extra Curricular}
\begin{list2}
\item \textbf {Karate} :- \textbf{Black Belt First Dan} trained in \textsl{Kyokushin Kai} for seven years. \textbf{District level champion} in \textsl{Kata} techniques. Stood \textbf {2\textsuperscript{nd}} in district level \textsl{Kumite}.
\item \textbf {Abacus} :- \textbf{Grand Master} in \textsl{Aloha Abacus and Speed Maths}. \textbf{Winner} at District, State and \textbf{National Level}.
\item \textbf {NIE Student of the Year '11} for all round performance. 
\item \textbf {Filmmaking} :- Actor in the winning video for \textsl{Freshiezza - Copy a Scene}, \textsl{Freshiezza - Music Video}, and lead actor in special mention video for \textsl{Freshiezza - Music Video}.
\item \textbf {Quizzes / Logic} :- \textbf{Winner} of \textsl{Whizz Kid '12}, \textbf{3\textsuperscript{rd}} at \textsl{Mood Indigo Treasure Hunt '14}, \textbf{2\textsuperscript{nd}} at \textsl{Rotary Club Logic Competition '10}, represented school at various \textbf{Inter-School quizzes}, \textbf{Finalist} at \textsl{Freshiezza Entertainment Quiz}
\pagebreak
\item \textbf {Football} :- Completed \textbf{NSO} (National Sports Organization) in Football. \textbf{Finalist} at \textsl{Fresher's Football League}. Part of \textbf{Inter Hostel General Championship team}.
\item \textbf {Other} :- \textbf{1\textsuperscript{th}} at \textsl {Wolf of Wall Street, E-Cell IIT Bombay}, \textbf{Designed Logo} for filmmaking YouTube channel,\textbf{Winner} at \textsl{Freshiezza - Band Imitation},  \textbf{Debator} at Intra-School Level, 

\item \textbf {Interests} :- \textbf{Star Gazing}, \textbf{Jogging}, \textbf{English Music} and \textbf{Travelling}. Have travelled to several countries in West and East Europe, Australia, New Zealand, Dubai, South Africa, Egypt and South East Asia.
\end{list2}



    

\end{resume}
\end{document}




	