\documentclass[11pt]{resume}

\title{Full resume}
\usepackage{hyperref}
\usepackage{graphicx}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    pdfborder={0 0 0},
}
\newcommand{\memph}[1]{#1}
%\newcommand{\memph}[1]{\textbf{#1}}
\begin{document}
\vspace*{20mm}
\vspace{-2em}
\begin{resume}

\section{\mysidestyle Academic Achievements}
\begin{list2}
\item Ranked \textbf {6\textsuperscript{th}} in the department among 140 students on CPI basis. \memph Pursuing a Minor Degree in Computer Science and Engineering.
\item Secured two \textbf {AP Grades} for being in the top 1\% of the courses \textbf{Basic Biology} and \textbf{Computer Programming and Utilization}.
\item Amongst the \textbf{top 10 in India} at the \textbf {Astronomy Olympiad OCSC} (Orientation Cum Selection Camp) for the International Olympiad for Astronomy and Astrophysics '14.
\item Cleared the first round of the \textbf{Physics Olympiad (NSEP)} and \textbf{Chemistry Olympiad (NSEC)} by being one amongst the top 300 in India.
\item Secured an All India Rank of \textbf{93} in \textbf{JEE Advanced '14} among 14 lakh candidates.
\item Secured an All India Rank of \textbf{34} in \textbf{JEE Mains '14} among 14 lakh candidates.
\item Secured a \textbf{National Rank of 2} in \textbf{ICSE '12} and was the \textbf{city topper} in  JEE Advanced '14, JEE Mains '14, CBSE '14 and KVPY '14.
\item Won the \textbf {Kishore Vaigyanik Protsahan Yojana '14 (KYPY)} Fellowship Award.
\item Awarded by the \textbf {Army Welfare Education Society} for the \textit{best academic performance} in Army Schools in CBSE '14. Won the \textit{General Proficiency Prize} for 10 years in school. 
\end{list2}

% Work Experience
\section{\mysidestyle Work Experience}
\textbf{Senior Backend Developer}, \textsl{Pickup} \hfill \textbf{March '14 - Present}

\begin{list2}
\item Developing the backend for a recently launched startup - \textit {Pickup}, a ridesharing service.
\item Built \textbf {RESTful APIs}, designed an \textbf {ER Model Database} in \textbf {PHP} using the \textit {MVC Framework} \textbf{Laravel 4}. Developing algorithms for the same.
\end{list2}

\textbf{In-sem Internship}, \textsl{Codechef} \hfill \textbf{January '15 - Feburary '15}\\
\vspace{-4mm}
\begin{list2}
\item Built and mantained a \textbf{question bank} as a part of \textbf {Codechef for Schools}, an initiative to help high school students start competitive programming.
\item Wrote and reviewed \textbf{editorials} for the recently added problems on Codechef.
\end{list2}

\section{\mysidestyle Positions of Responsibility}
\textbf{Convener}, \textit{Web and Coding Club - IIT Bombay} \hfill \textbf{April '14 - Present}\\

\vspace{-4mm}
\begin{list2}
\item \textbf{Coordinating events} of one of the largest programming clubs in India aimed at spreading the programming culture in the institute and helping newcomers.
\item Organised institute-wide workshops to \textbf{train more than 100 students} in MIT-Scratch and Linux Essentials.
\end{list2}

\textbf{Coordinator}, \textit{Mood Indigo - IIT Bombay} \hfill \textbf{July '15 - Present}\\
\vspace{-4mm}
\begin{list2}
\item Working as part of a team to develop \textbf{Web and Android applications} for Mood Indigo, Asia's largest college cultural festival. 
\end{list2}

\textbf{Mess Secretary}, \textit{Hostel 15 - IIT Bombay} \hfill \textbf{'14 - '15}\\
\vspace{-4mm}
\begin{list2}
\item Worked as a secretary to manage Mess affairs and voice student's opinion to the Mess Staff.
\end{list2}

\textbf{Mentor} \textit{XLR8, Robotics Club IIT Bombay} \hfill \textbf{August '15}

\begin{list2}
\item Mentored two teams in the largest technical event in IIT Bombay to build wireless remote controlled cars to be driven on an obstacle course.
\end{list2}
\vspace{-2.5mm}
\pagebreak
\section{\mysidestyle Extra Curricular}
\begin{list2}
\item \textbf {Karate} :- \textbf{Black Belt First Dan} trained in \textsl{Kyokushin Kai} for seven years. \textbf{District level champion} in \textsl{Kata} techniques. Stood \textbf {2\textsuperscript{nd}} in district level \textsl{Kumite}.

\item \textbf {Abacus} :- \textbf{Grand Master} in \textsl{Aloha Abacus and Aloha Speed Maths}, trained for 4 years. \textbf{Winner} at District, State and \textbf{National Level}. 

\item \textbf {NIE Student of the Year '11} for all round performance. 

\item \textbf {Filmmaking} :- Actor in the winning video for \textsl{Freshiezza - Copy a Scene}, \textsl{Freshiezza - Music Video}, and lead actor in special mention video for \textsl{Freshiezza - Music Video}.

\item \textbf {Football} :- Completed \textbf{NSO} (National Sports Organization) in Football. \textbf{Finalist} at \textsl{Fresher's Football League}. Part of \textbf{Inter Hostel General Championship team}.

\item \textbf {Quizzes / Logic} :- \textbf{Winner} of \textsl{Whizz Kid '12}, \textbf{3\textsuperscript{rd}} at \textsl{Mood Indigo Treasure Hunt '14}, \textbf{2\textsuperscript{nd}} at \textsl{Rotary Club Logic Competition '10}, represented school at various \textbf{Inter-School quizzes}, \textbf{Finalist} at \textsl{Freshiezza Entertainment Quiz}

\item \textbf {Other} :- \textbf{1\textsuperscript{th}} at \textsl {Wolf of Wall Street, E-Cell IIT Bombay}, \textbf{Designed Logo} for filmmaking YouTube channel,\textbf{Winner} at \textsl{Freshiezza - Band Imitation},  \textbf{Debator} at Intra-School Level, 

\end{list2}
\section{\mysidestyle Programming Skills}
\begin{list2}
\item \textbf{Languages:} PHP (with Laravel 4), C/C++, Python (with Django and OpenCV), Java (with Android), JavaScript (with NodeJS and AngularJS), Arduino, Bash, \LaTeX
\item \textbf{Tools:} NgSpice, Adobe Photoshop, AutoCAD, Git, MATLAB/Octave, Processing
\end{list2}



\section{\mysidestyle Technical Achievements} 
\begin{list2}
\item Adjudged the \textbf{Runner Up} (as part of a 4-person team) at the \textbf{Microsoft code.fun.do Hackathon '15}

\item Stood \textbf {7\textsuperscript{th}} in the country in \textbf {Technothlon '10} and represented my school with a teammate in \textbf {Techniche '10, IIT Guwahati}. 

\item Attended a 2 week long workshop \textbf{Infosys, Catch Them Young} and won the best group software award. 



\end{list2}


% Achievements


\section{\mysidestyle Projects}
\textbf{Pyraminx Utility Kit} \hfill \textbf{Spring '15}\\
\textsl{Prof. Kavi Arya} \hfill \textsl{CS 101 Project}\\
\vspace{-4mm}
\begin{list2}
\item Implemented \textbf{BFS graph algorithm and AVL trees} to derive mathematical results about the \textbf{optimal solutions of a Pyraminx}, a tetrahedron Rubiks Cube style puzzle.
\end{list2}
\textbf{Bluetooth Mesh Network} \hfill \textbf{Summer '15}\\
\textsl{Web and Coding Club - IIT Bombay} \hfill \textsl{Institute Technical Summer Project}\\
\vspace{-4mm}
\begin{list2}
\item \textbf{Android app} doing \textbf{routing via Bluetooth} using \textbf{Gnutella flooding algorithm}.
\end{list2}

%\end{list2}


\section{\mysidestyle Personal Projects}

\begin{list2}
\item \href{httpss://bugzilla.mozilla.org/user_profile?login=kalpeshk2011\%40gmail.com}{Contributing} to \textbf{Mozilla}, via bug fixes in Firefox Core, Firefox OS, Toolkit.
\item Active member on \textbf{Github} with a number of personal projects in \textsl{image processing, Python scripting, BASH, NodeJS and Javscript}.

\end{list2}
\section{\mysidestyle Interests} \textbf{Star Gazing}, \textbf{Jogging}, \textbf{English Music}, \textbf{Reading} and \textbf{Travelling}. Have travelled to several countries in West and East Europe, Australia, New Zealand, Dubai, South Africa, Egypt and South East Asia.

\textit{\textbf{Self motivated, passionate and always striving towards excellence.}}




    

\end{resume}
\end{document}




	