%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document
\setlength{\textheight}{11.1in}
\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------

\begin{resume}
\vspace*{17mm}
%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{SCHOLASTIC}  

Ranked \textbf{3\textsuperscript{rd}} in the department. Pursuing a Minor in \textbf{Computer Science}\\
Secured three \textbf{AP} grades(top 1\%) Data Analysis and Basic Programming, Biology.\\
Ranked \textbf{93\textsuperscript{rd}} in India among 1.5 lakh candidates in JEE Advanced '14.\\
Ranked \textbf{34\textsuperscript{th}} in India among 1.4 million candidates in JEE Mains '14.\\
\textbf{Top 10} in India in the 3\textsuperscript{rd} round of the \textbf{Astronomy Olympiad}, the OCSC.\\
\textbf{Top 300} in India in 1\textsuperscript{st} round of Physics Olympiad and Chemistry Olympiad.\\
Winner of the \textbf{Kishore Vaigyanik Protsahan Yojana '14} Fellowship Award.\\
\textbf{2\textsuperscript{nd}} in ICSE '12 (\textbf{98.6\%}). City topper in  CBSE '14 (\textbf{98.2\%}), JEE Advanced, Mains.\\
\textit{Army Welfare Education Society Prize} for best academic performance in Army Schools.

 
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{COMPUTER \\ SKILLS} 

{\sl Languages:} PHP(in Laravel 4), C/C++, Python(with OpenCV, Django), Java(with Android), Javascript(with NodeJS and AngularJS), Arduino, BASH\\
{\sl Software:} NgSpice, AutoCAD, Git, Wireshark, Photoshop, MATLAB, Processing
 
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Core Backend Developer}, \textbf{Pickup} \hfill March '15 - Present\\
 % Reduce space between items
Built \textbf {RESTful APIs}, designed an \textbf {ER Model Database} in \textbf {PHP} using the \textit {MVC Framework} \textbf{Laravel 4}. Developing algorithms for the same.

 
{\sl Convener}, \textbf{Web and Coding Club, IIT Bombay} \hfill April '15 - Present \\
Taking sessions and coordinating events of the largest programming club in India.

{\sl In-sem Intern}, \textbf{Codechef} \hfill January '14 - February '14 \\
Made problems for Codechef for Schools initiative and wrote algorithmic editorials.

{\sl Coordinator}, \textbf{Mood Indigo '15, IIT Bombay} \hfill July '15 - Present \\
Designing the website, Android application and other microsites for the festival.


\section{PROJECTS}

{\sl Web Platform Tests Viewer}, \textbf{Mozilla Quarter of Contribution} \hfill Winter '15 \\
Web app in AngularJS and IndexedDB to carry out efficient filtering and comparisons between WPT results in different browsers such as Gecko and Servo.

{\sl Pyraminx Utility Kit}, \textbf{CS 101 Project} \hfill Spring '15 \\
Used \textbf{BFS algorithm} and AVL trees to get mathematical results of optimal solutions of Pyraminx. Designed interface in C++, Allegro to get solve analysis, cube algorithm generators. Made \textbf{Android app} to read Pyraminx states via \textbf{image processing}.

{\sl Bluetooth Mesh Network}, \textbf{ITSP '15} \hfill Summer '15 \\
\textbf{Android} chat application to implement \textbf{routing via Bluetooth} using a \textbf{Gnutella styled flooding algorithm}. Used graph algoritms to optimize the same.

\section{OPEN SOURCE}
\textbf{Actively contributing to Mozilla} in Automation Team, Firefox OS and Fennec.\\ 
\textbf{Active member on Github} with a number of personal projects in \textit{image processing, Javascript, Python, NodeJS, Arduino.} Made the first ever Hindi guide for Git.
%---------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EXTRA-CURRICULAR \\ ACHIVEMENTS} 
Technical
\begin{itemize}\itemsep -13pt
\item\textbf{2\textsuperscript{nd}} at Microsoft code.fun.do Hackathon '14 for \textbf{PNR predictor} Windows app.\\
\item Attended \textbf{Infosys} Catch Them Young '10 and won best group software award.\\
\item 7\textsuperscript{th} in India at \textbf{Technothlon, Techniche '10, IIT Guwahati}.
\end{itemize}
Non Technical 
\begin{itemize}\itemsep -13pt
\item \textbf{Karate Black Belt First Dan}. Trained in \textit{Kyokushin Kai} for 7 years.\\
\item Grand Master in Aloha \textbf{Abacus and Speed Maths}. National level winner.\\
\item \textbf{NIE Student of the Year '11} for all round performance.\\
\item Finalist at Fresher Football League. Member of Inter-Hostel football team.\\
\item Interested in filmmaking, reading, music, star gazing, jogging and travelling.
\end{itemize}

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}